Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-07-06 Scripts/Initial_Analysis.Rmd
small changes

  # Reads taxon data
  proportion_data <- fread(paste(my_path("R",extra_path = "Proportion/"),"proportion_",taxon_key,".csv", sep=""))

  if(links == "y"){
    # summarizes by country and neighbour
    country_summary <- proportion_data %>% 
      group_by(taxon_key,eez_name,eez_neighbour,time_step) %>% 
      summarise(
        mean_spp = mean(ensamble_mean,na.rm=T) # average spp change from all countries sharing
      )

  }else{
    # summarizes by country
    country_summary <- proportion_data %>% 
      group_by(taxon_key,eez_name,time_step) %>% 
      summarise(
        mean_spp = mean(ensemble_mean,na.rm=T) # average spp change from all countries sharing
      )
    }

@@

   eez_summary <- spp %>% 
     group_by(eez_name,eez_neighbour,time_step) %>% 
     summarise(
       n_spp = n(),
       min_spp = min(mean_spp,na.rm=T),
       max_spp = max(mean_spp,na.rm=T),
       sd_spp = sd(mean_spp,na.rm=T), # for some weird reason it wont work if the order is fliped
       mean_spp = mean(mean_spp,na.rm=T)
     ) %>% 
     select(eez_name:max_spp,mean_spp,sd_spp)

@@

   eez_summary <- spp %>% 
   group_by(eez_name,time_step) %>% 
   summarise(
     n_spp = n(),
     min_spp = min(mean_spp,na.rm=T),
     max_spp = max(mean_spp,na.rm=T),
     sd_spp = sd(mean_spp,na.rm=T), # for some weird reason it wont work if the order is fliped
     mean_spp = mean(mean_spp,na.rm=T)
   ) %>% 
   select(eez_name:max_spp,mean_spp,sd_spp)

@@

 proportion_change <- eez %>% 
   gather("variable","value",n_spp:sd_spp) %>% 
   spread(time_step,value) %>% 
   mutate_at(vars(
     "per_mid" = mid,
     "per_end" = n_end),
            funs(round((((.-historical)/historical))*100,2))
   )

@@

# Get taxon list
Taxon_List <- list.files(paste(my_path("R"),"Proportion",sep=""))

@@

# Run results
results <- PropChange(Taxon_List, links="y") %>% 
  mutate(per_mid_plot =ifelse(per_mid >= 50, 50,
                           ifelse(per_mid <= -50,-50,per_mid)
                           )
         )

@@

# Prepare data from results
Data <- results %>% 
  # get coords for sources
  left_join(eez_centroid,
            by = "eez_name") %>%
  rename(source = eez_name,
         start_lon = longitude,
         start_lat = latitude,
         eez_name=eez_neighbour) %>% 
  # get coords for targets
  left_join(eez_centroid,
            by = "eez_name") %>% 
  rename(target = eez_name,
         end_lon = longitude,
         end_lat = latitude) %>% 
  ungroup() %>% 
  # Plot miscs
  mutate(
    per_mid = ifelse(is.na(per_mid_plot),0,per_mid_plot)
  ) %>% 
  drop_na() %>%
  filter(
    variable == "mean_spp"#,
    # source %in% c("Brazil","Argentina","Chile","Peru","Uruguay")
  )

@@

@@

@@

x <- ggplot() +
  geom_sf(data = subset(World_map, sovereignt != "Antarctica"), size = 0.1, fill = "gray90", col = "gray90") +
  geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray70") +
  geom_point(data = subset(Data, per_mid < 0),
             aes(start_lon,
                 start_lat,
                 col = per_mid),
             size = 0.05,
             col = "gray30",
             shape = 20,
             stroke = 1.5) +
  geom_path(data = subset(paths, per_mid > 0),
            aes(X, Y,
                group = interaction(line_id,subline_id),
                col = per_mid
            ),
            size = 0.3,
            arrow = arrow(length = unit(0.009, "npc"),
                          ends = "first"),
            show.legend = NA) +
  ggtheme_map() +
  scale_colour_viridis(
    name="Average Gain of\nStock-Share Ratio (%)",
    limits = c(0,max(Data$per_mid)),
    breaks = seq(0,max(Data$per_mid),5),
    # option="magma",
    direction = 1
  ) +
  ggsave("figure_connections_n50.png",
         width = 10,
         height = 6,
         units = "in"
  )

@@

# Load all sp in noe table
Eme_Res <- bind_rows(lapply(Paths, fread)) %>% 
  filter(
    n_ens == 10
  )
# warnings() for empty data species

@@

# The path
path_world <- paste(data_path,"Spatial/SAU_Shapefile/",sep="")

@@

# Per EEZs
eez_d_hist <- Eme_Res %>% 
  group_by(emerging_yr,eez_name) %>% 
  # summarise(n_tax = length(unique(taxon_key))) %>% 
  summarise(n()) %>% 
  mutate(
    level = "EEZ"
  ) %>% 
  select(1,3,4)

>>>>

  # Reads taxon data
  proportion_data <- fread(paste(my_path("R",extra_path = "Proportion_2005/"),"proportion_",taxon_key,".csv", sep=""))

  if(links == "y"){
    # summarizes by country and neighbour
    country_summary <- proportion_data %>% 
      group_by(taxon_key,eez_name,eez_neighbour,time_step) %>% 
      summarise(
        mean_spp = mean(ensemble_mean, na.rm = T) # average spp change from all countries sharing
      ) %>% 
      filter(!is.na(mean_spp))

  }else{
    # summarizes by country
    country_summary <- proportion_data %>% 
      group_by(taxon_key,eez_name,time_step) %>% 
      summarise(
        mean_spp = mean(ensemble_mean,na.rm=T) # average spp change from all countries sharing
      ) %>% 
      filter(!is.na(mean_spp))
    }

@@

   eez_summary <- spp %>% 
     group_by(eez_name,eez_neighbour,time_step) %>% 
     summarise(
       n_spp = n(),
       min_eez = min(mean_spp, na.rm=T),
       max_eez = max(mean_spp, na.rm=T),
       sd_eez = sd(mean_spp, na.rm=T), # for some weird reason it wont work if the order is fliped
       mean_eez = mean(mean_spp,na.rm=T)
     ) %>% 
     select(eez_name:max_eez,mean_eez,sd_eez)

@@

   eez_summary <- spp %>% 
   group_by(eez_name,time_step) %>% 
   summarise(
       n_spp = n(),
       min_eez = min(mean_spp, na.rm=T),
       max_eez = max(mean_spp, na.rm=T),
       sd_eez = sd(mean_spp, na.rm=T), # for some weird reason it wont work if the order is fliped
       mean_eez = mean(mean_spp,na.rm=T)
     ) %>% 
     select(eez_name:max_eez,mean_eez,sd_eez)

@@

 proportion_change <- eez %>% 
   gather("variable","value",n_spp:sd_eez) %>% 
   spread(time_step,value) %>% 
   mutate_at(vars(
     "per_early" = early,
     "per_mid" = mid
     ),
            funs(round((((.-historical)/historical))*100,2))
   )

@@

# Get taxon list
Taxon_List <- list.files(paste(my_path("R"),"Proportion_2005",sep=""))

@@

# Run results
results <- PropChange(Taxon_List, links="y") %>% 
  mutate(per_mid_plot =ifelse(per_mid >= 50, 50,
                           ifelse(per_mid <= -50,-50,per_mid)
                           ),
         per_early_plot =ifelse(per_early >= 50, 50,
                           ifelse(per_early <= -50,-50,per_early)
                           )
         )

@@

# Prepare data from results
Data <- results %>% 
  # get coords for sources
  left_join(eez_centroid,
            by = "eez_name") %>%
  rename(source = eez_name,
         start_lon = longitude,
         start_lat = latitude,
         eez_name=eez_neighbour) %>% 
  # get coords for targets
  left_join(eez_centroid,
            by = "eez_name") %>% 
  rename(target = eez_name,
         end_lon = longitude,
         end_lat = latitude) %>% 
  ungroup() %>% 
  # Plot miscs
  mutate(
    per_early = ifelse(is.na(per_early_plot),0,per_early_plot),
    per_mid = ifelse(is.na(per_mid_plot),0,per_mid_plot)
  ) %>% 
  drop_na() %>%
  filter(
    variable == "mean_eez"#,
    # source %in% c("Brazil","Argentina","Chile","Peru","Uruguay")
  )

@@

# Create data path for line connections
paths <- network_data_sf %>% 
  sf::st_set_geometry(NULL) %>% 
  unnest() %>% 
  mutate_at(vars(X,Y), round,2) %>% 
  gather("time_step","per_chng",per_mid_plot:per_early_plot)

@@

Data <- Data %>% 
  gather("time_step","per_chng",per_mid_plot:per_early_plot)

@@

# time <- "per_mid_plot"
time <- "per_early_plot"

x <- ggplot() +
  geom_sf(data = subset(World_map, sovereignt != "Antarctica"), size = 0.1, fill = "gray90", col = "gray90") +
  geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray70") +
  geom_point(data = subset(Data, time_step == time & per_chng < 0),
             aes(start_lon,
                 start_lat,
                 col = per_chng),
             size = 0.05,
             col = "gray30",
             shape = 20,
             stroke = 1.5) +
  geom_path(data = subset(paths, time_step == time & per_chng > 0),
            aes(X, Y,
                group = interaction(line_id,subline_id),
                col = per_chng
            ),
            size = 0.3,
            arrow = arrow(length = unit(0.009, "npc"),
                          ends = "first"),
            show.legend = NA) +
  my_ggtheme_m() +
  scale_colour_viridis(
    name="Average Gain of\nStock-Share Ratio (%)",
    limits = c(0,max(Data$per_chng)),
    breaks = seq(0,max(Data$per_chng),5),
    # option="magma",
    direction = 1
  ) +
  ggsave("./Figures/figure_connections_early_n50.png",
         width = 10,
         height = 6,
         units = "in"
  )

@@

# Load all sp in one table
Eme_Res <- bind_rows(lapply(Paths, fread)) %>% 
  filter(
    n_ens == 10
  )
# warnings() for empty data species

@@

@@

# Per EEZs
eez_d_hist <- Eme_Res %>% 
  group_by(eez_name,emerging_yr) %>% 
  # summarise(n_tax = length(unique(taxon_key))) %>% 
  summarise(n()) %>% 
  mutate(
    level = "EEZ"
  ) %>% 
  select(1,3,4)
